--- 
title: "Example of Using External Code with source" 
author: "[Ben Marwick](http://faculty.washington.edu/bmarwick/)"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: bookdown::html_document2
--- 

```{r setup, include=FALSE} 
knitr::opts_chunk$set(echo = TRUE) 
``` 

The code chunk shows that we cannot easily show the code in the external script file using `source()`.

```{r RunCodeChunkNoEval, eval=FALSE} 
source('my-external-code.R')
``` 

The code chunk executes the externally located code using `source()`. When using this method, we cannot easily print the code. Text output is suppressed because we are using `results='hide'` and figures are plotted, but only after all of the code is executed. 

```{r RunCodeChunk, results='hide'} 
source('my-external-code.R')
``` 

The code chunk executes the externally located code using `source()`. When using this method, we cannot easily print the code. Text output is only for objects that we use `print()` on. And figures are plotted, but only after all of the code is executed. 

```{r RunCodeChunkShowAll, echo=FALSE} 
source('my-external-code.R')
```

This code chunk will pass the source code and fully print and evaluate all code in the external script

```{r code = readLines('my-external-code.R')}
```

